---
title: "Course 9 - Week 2 project"
author: "Wellintton Perez"
date: "11/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE}
library(data.table)
library(leaflet)
library(dplyr)
```

## Introduction

I am using the data set for a data analytic project I worked on for a non-profit called
[Classroom, Inc.](https://www.classroominc.org/) Please check them out they do great work in the less fortunate
communities accross the USA and the world. The interactive map shows the distribution of student in the United States.  For this map I am only using the United States data.

```{r echo=FALSE, message=FALSE}
data<-fread("dateset-latlon.csv",sep=",",stringsAsFactors = FALSE,nrows=-1)

top_5_states <- data[order(-data$count)][1:5]
labels <- c(paste(top_5_states$state,top_5_states$count,sep=": "))
```

### Classroom, Inc. Student distribution

The map shows the states where Classroom, Inc has affiliated with local schools to allow students to play the games.

- Click on the cluster to drill down on the states
- You can click on the blue circles to see the number of students in that state
- The legend shows the top 5 states 

```{r echo=FALSE, message=FALSE}
data %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers( lat=data$lat, lng=data$lng,popup = c(as.character(data$count)), 
             clusterOptions =markerClusterOptions()) %>% 
  addLegend(labels = labels, colors = c("", "", "","",""),title="Top 5 State")
````

